---
title: "Trend of Flight Safety and Detection of Causes of Fatal Air Accidents Using Text Mining Techniques"
author: "Kaiwei Qian"
date: "2019/5/6"
output: 
  pdf_document:
    number_sections: true
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(magrittr)
library(tidyverse)
library(RCurl)
library(jsonlite)
library(tidytext)
library(lubridate)
library(wordcloud)
```

# Introduction

On March 4, a Boeing 737 MAX 8 crashed during the climb killing 157 people without survivor. 5 months before, an aircraft, still a Boeing 737 MAX 8, dove into the sea and crashed, killing all the 189 people on board. These two air accidents are reported to be related to the flawed Maneuvering Characteristics Augmentation System (MCAS) [@nyt]. Recent fatal air crashes arouse my concern for aviation safety, especially for commercial flights. Air accidents dataset and statistics of commercial flights are utilized to analysze the trend of flight safety. In addition, text mining techniques are employed to detect the factors that are mostly likely to induce fatal air accidents.

There are 6 sections in this report. Data and the ways how they are collected from Internet are described in Section 2. Exploratory analysis is performed in Section 3. In Section 4, the trend of flight safety is studied for the past 10 years (2009-2018), followed by Section 5, where text mining techniques are tried to extract the keywords from the cause of air accidents. The last section gives the conclusion of the project.

In addition, please refer to https://github.com/KaiweiQian/air-crash-analysis for the code and data of this project.

# Data

## Aircraft Accidents Dataset

```{r get.air.crash.data, results='hide', eval=FALSE, echo=FALSE}
# the url for the air accidents from 2009-01-01 to 2018-12-31
url.air.accident <- "http://www.baaa-acro.com/crash-archives?created=2009-01-01&created_1=2018-12-31&field_crash_region_target_id=All&field_crash_country_target_id=&field_crash_registration_target_id=&field_crash_aircraft_target_id=&field_crash_operator_target_id=&field_crash_cause_target_id=All&field_crash_zone_target_id=&field_crash_site_type_target_id=All&field_crash_phase_type_target_id=All&field_crash_flight_type_target_id=All&field_crash_survivors_value=All&field_crash_city_target_id="

tbl_air_accident_raw <- NULL
# we know that it has 14 pages.
for(page in 0:13) {
  tmp.url <- paste(url.air.accident, "&page=", page, sep="")
  # Find the node contain the table
  new_tbl_node <- read_html(tmp.url) %>%
    html_node(xpath = '/html/body/div[1]/div[4]/div/section/div[2]/div/div/div[3]/div/table') 
  # There is a red plus at the end of each row. It leads the users to the detail page. So, we choose to save the url and later we'll go to this website for the detailed report.
  new_tbl_detail_url <- new_tbl_node %>% 
    html_nodes(xpath = '/html/body/div[1]/div[4]/div/section/div[2]/div/div/div[3]/div/table/tbody/tr/td[8]/a/@href') %>%
    html_text()
  
  new_tbl <- new_tbl_node %>%
    html_table %>%
    select(Date, `A/C Type`, Location, Fatalities, Registration) %>%
    mutate(detail.url = paste("http://www.baaa-acro.com", new_tbl_detail_url, sep = ""))
  
  tbl_air_accident_raw <- rbind(tbl_air_accident_raw, new_tbl)
}

# save this dataframe to csv.file
write_csv(tbl_air_accident_raw, path = "./Intermediate Results/air_accident_table_2009-2018.csv")

rm(list=ls()); gc()
```


```{r get.air.crash.detail, results='hide', eval=FALSE, echo=FALSE}
tbl_air_accident_raw <- read_csv("./Intermediate Results/air_accident_table_2009-2018.csv")

detail.url <- tbl_air_accident_raw$detail.url

tbl_air_accident_raw$`Flight Phase` = ""
tbl_air_accident_raw$`Circumstances` = ""
tbl_air_accident_raw$`Flight Type` = ""
tbl_air_accident_raw$`Site` = ""
tbl_air_accident_raw$`Probable cause` = ""

# this loop can be very time-consuming, I'd recommend you don't run it.
for(i in 1:length(detail.url)) {
  print(i)
  tmp.url <- detail.url[i]
  tmp.html <- read_html(tmp.url)
  # save Flight Phase
  tbl_air_accident_raw$`Flight Phase`[i] <- tmp.html %>%
    html_node(xpath = '/html/body/div[1]/div[3]/div/section/div[2]/article/div/div[2]/div[@class="crash-flight-phase"]/a/div') %>%
    html_text()
  # Flight Type
  tbl_air_accident_raw$`Flight Type`[i] <- tmp.html %>%
    html_node(xpath = '//div[@class="crash-flight-type"]/a/div') %>%
    html_text()
  # Site
  tbl_air_accident_raw$`Site`[i] <- tmp.html %>%
    html_node(xpath = '//div[@class="crash-site"]/a/div') %>%
    html_text()
  # set the Circumstance and Probable Cause
  tmp_circum_and_cause <- tmp.html %>%
    html_nodes(xpath = '//div[@class="crash-circumstances"]/div') %>%
    html_text()
  tmp_circum <- tmp_circum_and_cause[1]
  
  if(length(tmp_circum_and_cause) == 2) {
    tmp_cause <- tmp_circum_and_cause[2]
  } else tmp_cause = ""
  # Circumstances
  tbl_air_accident_raw$`Circumstances`[i] <- tmp_circum
  # Probable cause
  tbl_air_accident_raw$`Probable cause`[i] <- tmp_cause
}

# save this dataframe to csv.file
write_csv(tbl_air_accident_raw, path = "./Intermediate Results/air_accident_table_with_detail_2009-2018.csv")
rm(list=ls()); gc()
# Save it as an intermediate result.
```

The data used in this study is scraped from the __Bureau of Aircraft Accidents Archives__ (http://www.baaa-acro.com/crash-archives) for the past 10 years (2009-2018). The Bureau of Aircraft Accidents Archives (BAAA) was established in Geneva in 1990 for the purpose to deal with all information related to aviation accidentology.

Scraping involves two steps.

First, After __read_html()__ reads the string-type HTML from the response, __html_node(xpath = '/html/body/div[1]/div[4]/div/section/div[2]/div/div/div[3]/div/table')__ locates the table that contains the information of the air accidents, such as Date, A/C Type, Location, Fatalities and Registration. Detailed explanation of these variables are shown in Table 1. 

If you visit their website, you'll find that there is a plus sign at the end of each row of the table. Clicking on it leads you to the page that briefly summarizes the air crash. It provides more detailed information, such as Flight Phase and Circumstances. So, I choose to keep the hyperlinks to this page. __html_nodes(xpath = '/html/body/div[1]/div[4]/div/section/div[2]/div/div/div[3]/div/table/tbody/tr/td[8]/a/@href')__ locates the column of the hyperlinks belonging to and __html_text()__ reads the data from that column.

In the second step, the spider visits each page that contains a brief summary of air crashes. I choose to keep the records of Flight Phase, Flight Type, Site, Circumstances and Probable Causes (if exists) for further study. Circumstances and Probable Causes are mainly used to support the text mining part of this project. XPath is used to read the data from the HTML.

Note that instead of air crashes, this dataset include all the records of air accidents, which means the plane may not be necessarily hit land or water and be damaged. For example, some mechanical problems during the flight are also deemed as air accidents.

```{r read.air.crash.data, message=FALSE, echo=FALSE}
# read the data
df_air_crash <- read_csv("./Intermediate Results/air_accident_table_with_detail_2009-2018.csv")

# convert the date from String to Date and remove the column of detail.url
df_air_crash <- df_air_crash %>%
  mutate(Date = mdy(Date), detail.url = NULL)
```

```{r air.crash.description, echo=FALSE}
des_air_crash <- tibble(`Variable Name` = names(df_air_crash),
                        `Data Type` = sapply(df_air_crash, class),
                        Description = "")
des_air_crash$Description[1] = "The date when the accident occurred"
des_air_crash$Description[2] = "The type of the aircraft"
des_air_crash$Description[3] = "The location where the accident occurred"
des_air_crash$Description[4] = "Number of deaths caused by the accident"
des_air_crash$Description[5] = "A unique ID for the airplane"
des_air_crash$Description[6] = "Flight phase during which the accident occurred"
des_air_crash$Description[7] = "A breif description of the circumstances where the accident occurred"
des_air_crash$Description[8] = "The type of this flight; can be private, commercial and so on"
des_air_crash$Description[9] = "Description of the location where the air crash occurred"
des_air_crash$Description[10] = "Possible causes given by the investigation by NTSB"

knitr::kable(des_air_crash, booktabs = TRUE, caption = "Description of the variables in BAAA Air Accidents dataset.")
```

## Flight Statistics

The flight statistics dataset is scraped from __Statista__. The number of flights performed by the global airline industry from 2009 to 2018 and the number of scheduled passengers boarded by the global airline inudstry from 2009 to 2018 are collected from https://www.statista.com/statistics/564769/airline-industry-number-of-flights and https://www.statista.com/statistics/564717/airline-industry-passenger-traffic-globally, respectively. 

In each of websites mentioned above, there are two tables, which contain the number of scheduled commercial flights and the number of passengers and the number of scheduled passengers boarded from 2004 to 2019, respectively. For each of the websites, __html_node(xpath = '//table')__ locates the table, and __html_table()__ reads the table from its HTML structure. 

Only the records from 2009 to 2018 are used in this project in order to keep them consistent with the air accidents dataset in terms of time range. Moreover, the numbers from __Statista__ are only for the commercial flights while the air accidents dataset also contain the records for private, cargo and other flights. So, it's essential to keep the difference of these two data sources in mind and avoid causing confusion.

```{r get.num.of.flight, results='hide', eval=FALSE, echo=FALSE}
# If this links give you "- -", you can just try another time...
num.of.flight.url <- "https://www.statista.com/statistics/564769/airline-industry-number-of-flights"
tbl_num_of_flight <- num.of.flight.url %>%
  read_html() %>%
  html_node(xpath = '//table') %>%
  html_table()
# change the variable name
names(tbl_num_of_flight) <- c("year", "number of flights")

tbl_num_of_flight <- tbl_num_of_flight %>%
  mutate(`number of flights` = `number of flights` * 1e+6,
         year = as.numeric(str_extract(year, '\\d{4}'))) %>%
  filter(year >= 2009 & year <= 2018)
# save 
write_csv(tbl_num_of_flight, path = "./Intermediate Results/global_num_of_flights_2009-2018.csv")
rm(list=ls()); gc()
```

```{r get.num.of.passenger, results='hide', eval=FALSE, echo=FALSE}
# If this links give you "- -", you can just try another time...
num.of.passenger.url <- "https://www.statista.com/statistics/564717/airline-industry-passenger-traffic-globally"
tbl_num_of_passenger <- num.of.passenger.url %>%
  read_html() %>%
  html_node(xpath = '//table') %>%
  html_table()
# change the variable name
names(tbl_num_of_passenger) <- c("year", "number of passengers")

tbl_num_of_passenger <- tbl_num_of_passenger %>%
  mutate(`number of passengers` = (`number of passengers` %>% 
                                     str_remove_all(pattern = ",") %>%
                                     as.numeric() * 1e+6), 
         year = as.numeric(str_extract(year, '\\d{4}'))) %>%
  filter(year >= 2009 & year <= 2018)
# save 
write_csv(tbl_num_of_passenger, path = "./Intermediate Results/global_num_of_passengers_2009-2018.csv")
rm(list=ls()); gc()
```

# Exploratory Analysis

## Aircraft Type

The number of air accident records is `r dim(df_air_crash)[1]`. And, there are `r dim(df_air_crash)[2]` variables for each record. The `r dim(df_air_crash)[2]` variables are `r paste(names(df_air_crash), collapse = ", ")`.

Barplots are employed to see what types of aircraft is involved in most air accidents and what types of aircraft cause the most fatalities. After grouping the data by __A/C Type__, I sum the __Fatalities__ and count the number of air accidents for each type of aircraft. __gather()__ and __facet_wrap()__ are used to generate these two plots. 

Top 10 aircraft types are shown in Figure 1. __Boeing 777-200__ has caused the most deaths and __PZL-Mielec AN-2__ has been involved in the most accidents in the past 10 years. Interestingly, the A/C Type which causes hundreds of deaths are not among the types which are most often involved in accidents, except for __Lockheed C-130 Hercules__. One possible reason for this phenomenon is that __Boeing__ and __Airbus__ produce commercial airplanes that can contain hundreds of people and several fatal air accidents can lead to hundreds of fatalities. 

Thus, the difference in aircraft capacity must be taken in to consideration when we evaluate the flight safety. 

```{r exploratory.by.type.plot, echo=FALSE, fig.cap = "Frequency and Fatalities of Air Accidents by Aircraft Type."}
crash_by_type <- df_air_crash %>%
  group_by(`A/C Type`) %>%
  summarize(fatalities = sum(Fatalities), times = n()) %>%
  gather(key = "Variable Name", value = "n", -`A/C Type`) %>%
  group_by(`Variable Name`) %>%
  mutate(rank = min_rank(desc(n))) %>%
  filter(rank <= 10)

ggplot(data = crash_by_type, mapping = aes(x = `A/C Type`, y = n)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~`Variable Name`, scales = "free", dir = "v") +
  xlab("aircraft type") + ylab("number") +
  coord_flip() 
```


## Flight Phase

Barplots in Figure 2 shows that nearly half of the accidents that occur during the landing phase. Though only 1/4 of the total air accidents happen during the flight, the fatalities caused in this phase are as many as that those caused during the landing phase. 

When the plane is landing, it has lower speed and lower altitude. So, even the airplane accidents during the landing or approaching phase occur more often than during flight, the chance of surviving must be higher than the accident in the sky. What's more, landing or approaching means that the plane is near an airport, where the people are ready for any emergency situation. 

```{r exploratory.by.phase.plot, echo=FALSE, fig.cap = "Frequency and Fatalities of Air Accidents by Flight Phase.", fig.height=4, fig.width=7}
crash_by_phase <- df_air_crash %>%
  group_by(`Flight Phase`) %>%
  summarize(fatalities = sum(Fatalities), times = n()) %>%
  gather(key = "Variable Name", value = "n", -`Flight Phase`) %>%
  group_by(`Variable Name`) %>%
  mutate(rank = min_rank(desc(n)))

ggplot(data = crash_by_phase, mapping = aes(x = `Flight Phase`, y = n)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~`Variable Name`, scales = "free", dir = "v") +
  xlab("flight Phase") + ylab("number") + 
  coord_flip() 
```


```{r exploratory.by.location.plot, echo=FALSE}
# seems to be meaningless
crash_by_location <- df_air_crash %>%
  group_by(`Location`) %>%
  summarize(fatalities = sum(Fatalities), times = n()) %>%
  gather(key = "Variable Name", value = "n", -`Location`) %>%
  group_by(`Variable Name`) %>%
  mutate(rank = min_rank(desc(n))) %>%
  filter(rank <= 10)

#ggplot(data = crash_by_location, mapping = aes(x = `Location`, y = n)) + 
  #geom_bar(stat = "identity") + 
  #facet_wrap(~`Variable Name`, scales = "free") +
  #xlab("Location") + ylab("Number") + coord_flip()
```

# Time Series for Commercial Flights

```{r show.ts.crash, echo=FALSE, message = FALSE, fig.cap="Number of Air Accidents and Fatalities per Year", fig.height=4, fig.width=7}
crash_by_year <- df_air_crash %>%
  mutate(Date = year(Date)) %>%
  group_by(Date) %>%
  summarize(fatalities = sum(Fatalities), times = n()) %>%
  gather(key = "Variable Name", value = "n", -`Date`) 

ggplot(data = crash_by_year, mapping = aes(x = `Date`, y = n)) + 
  geom_point() + geom_line() +
  facet_wrap(~`Variable Name`, scales = "free", dir = 'v') +
  xlab("year") + ylab("number") 
```

```{r show.ts, echo=FALSE, message = FALSE, fig.cap="Number of Commercial Flights and Passengers per Year.", fig.height=4, fig.width=7}
df_n_flights <- read_csv("./Intermediate Results/global_num_of_flights_2009-2018.csv")
df_n_passengers <- read_csv("./Intermediate Results/global_num_of_passengers_2009-2018.csv")

df_flight_stat <- df_n_flights %>%
  left_join(df_n_passengers, by = "year") %>%
  gather(key = "variable", value = "n", -year)

ggplot(data = df_flight_stat, mapping = aes(x = year, y = n/1000000)) + 
  geom_point() + geom_line() + facet_wrap(~variable, scale = "free", dir = 'v') + ylab("number in million")
```

In this section, records are grouped by year, and I'm interested in the trend of the fatalities and number of air accidents from 2009 to 2018. In addition, the number of scheduled flights and the number of passengers boarded are used to normalize the air accidents dataset in order to achieve fair evalution of flight safety.

Figure 3 indicates that the fatalities related to air accidents fluctuate around 800 per year, and the number of air accidents has deacreased from 160 to 110 from 2009 to 2018. The problem is whether fluctuating fatalities caused by air crashes each year indicates no improvement in flight safety.

Figure 4 shows that the number of commercial flights scheduled and number of passengers each year has been increasing in the past ten years. Therefore, it's more appropriate to evaluate the flight safety by the ratio of fatalities to the number of passengers aboard and __fatal accident rate__, which is the ratio of number of fatal air accidents to the total number of flights, because they're normalized and can fairly reflect the true trend of flight safety.

Note that the data of the number of flights and passengers are only for commercial flights. Therefore, only the air accidents with the flight type of "Scheduled Revenue Flight" can be used to calculate those ratios for commercial flights.

## Fatalities per Passengers Boarded

```{r show.ts.fata.per.pass, echo=FALSE, message = FALSE, fig.cap="Fatalities per Passengers Boarded per Year.", fig.width = 7, fig.height=3.5}
fata_per_pass <- df_air_crash %>%
  filter(`Flight Type` == "Scheduled Revenue Flight") %>%
  mutate(year = year(Date)) %>%
  group_by(year) %>%
  summarize(fatalities = sum(Fatalities)) %>%
  left_join(df_n_passengers, by = "year") %>%
  mutate(ratio = fatalities/`number of passengers`*1e+6)

ggplot(data = fata_per_pass, mapping = aes(x = year, y = ratio)) + 
  geom_point() + geom_line() + ylab("fatalities per one million passengers") + xlab("year")
```

Figure 5 shows a downward trend for the number of victims per one million passengers for commercial flights. 2014 and 2018 are two abnormal years because the number of fatalities do not follow the overall trend for these two years. In 2018, there were two major air crashed that caused more than 300 deaths. One of them is the Boeing 737 MAX 8 that crashed in Jakarta and killed 189 people. In 2014, there were three air crashes that involved Boeing and Airbus. These three major accidents killed 162, 298 and 239, respectively.

## Fatal Accident Rate

```{r show.ts.fata.acc.rate, echo=FALSE, message = FALSE, fig.cap="Fatal Accident Rate per Year.", fig.width = 7, fig.height=3.5}
fata_acc_rate <- df_air_crash %>%
  filter(Fatalities > 0 & `Flight Type` == "Scheduled Revenue Flight") %>%
  mutate(year = year(Date)) %>%
  group_by(year) %>%
  count() %>%
  left_join(df_n_flights, by = "year") %>%
  mutate(ratio = n/`number of flights`*1e+6)

ggplot(data = fata_acc_rate, mapping = aes(x = year, y = ratio)) + 
  geom_point() + geom_line() + ylab("fatal accidents per one million flights") + xlab("year")
```

Figure 6 indicates that the number of air accidents that caused deaths per one million flights has been decreasing in the past ten years. However, the decreasing fatal accidents rate does not necessarily mean that the number of victims related to air crash also goes down. It's clear that Figure 6 fails to capture the extremely high fatalities in 2014 and 2018. Though the number of crashes was normal in 2014 and 2018, it is because those accidents involved high-capacity commercial airplanes. 

```{r std.cor.plot, echo=FALSE, warning=FALSE, fig.height=4.3, fig.width=7, fig.cap="Relation between the Number of Fatal Air Crashes Involving Boeing and Airbus and Fatalities per One Million Passengers per Year"}
num_boeing_airbus_fatal <- df_air_crash %>%
  filter(Fatalities > 0 
         & (str_detect(`A/C Type`, '\\bBoeing\\b') | str_detect(`A/C Type`, '\\bAirbus\\b')) 
         & `Flight Type` == "Scheduled Revenue Flight") %>%
  mutate(year = year(Date)) %>% 
  group_by(year) %>%
  count()

cor_n_ratio <- left_join(fata_per_pass, num_boeing_airbus_fatal, by="year") %>%
  select(year, n, ratio)

cor_n_ratio$n[which(cor_n_ratio$year==2017)] = 0

plot_n_ratio <- cor_n_ratio %>%
  mutate(n = scale(n), ratio = scale(ratio)) %>%
  gather(key = "variable", value = "value", -year)

ggplot(data = plot_n_ratio, mapping = aes(x = year, y = value, color = variable)) + 
  geom_point() + geom_line() + ylab("standardized value") +
  scale_color_discrete(labels = c("number of air crashes", "fatalities per one million passengers")) + 
  theme(legend.position=c(0.78, 0.9))
```

Furthermore, Figure 7 indicates the strong correlation between fatalities per one million passengers and the fatal accidents involving Boeing and Airbus, and its correaltion is `r cor(cor_n_ratio$ratio, cor_n_ratio$n)`. 

__str_match()__ is used to select the fatal accidents that involved Airbus and Boeing along with __filter()__. Regular expressions used here are __\\bBoeing\\b__ and __\\bAirbus\\b__. Two variables included in Figure 7 are scaled with respect to their mean and standard deviation, respectively. Since there was no fatal accident related to these two giant manufacturers in 2014, the number of accidents for that year should be set equal to 0 manually, instead of leaving it N/A.

In conclusion, except for some extreme years, the commerical flights have become safer over the past ten years in terms of fatalities per one million passengers. In addition, the rate of fatal accidents keeps going down. However, air crashes that involve high-capacity planes, such as Boeing and Airbus, lead to significant increase in the fatalities. 

# Text Mining

BAAA provides information of the circumstances when the air accident happened and there would be one section called "Probable cause" if the investigation had been done. I'm interested in the key factors that lead to fatal air accidents and try to use text mining techniques to detect them. 

Since the investigation of some fatal accidents has not been completed, there is no __Probable cause__, i.e. its value is N/A. Instead of leaving a lot of blanks, __ifelse()__ is used to substitute the __Circumstances__ for __Probable causes__ for those unclosed investigations. Since commercial flights are more relevant to our daily life, I decide to investigate the causes of air crashes with __Flight Type__ of "Scheduled Revenue Flight". __filter()__ helps select those air accidents related to commercial flights.

N-gram model, including n = 1, is the major tool I use in this section.

```{r unite.desc, echo=FALSE}
# load the stop_words dataset, we'll remove the stop-words in the detain later.
data("stop_words")

desc_accident <- df_air_crash %>%
  filter(`Flight Type` == "Scheduled Revenue Flight") %>%
  #filter(str_detect(`A/C Type`, '\\bBoeing\\b') | str_detect(`A/C Type`, '\\bAirbus\\b')) %>%
  #unite(description, Circumstances, `Probable cause`, sep = " ")
  mutate(description = ifelse(Fatalities > 0 & !is.na(`Probable cause`), `Probable cause`, Circumstances)) %>%
  select(description, Fatalities) 
```

## Single Word

```{r word.count, echo=FALSE, fig.cap="Word Cloud for Top 30 Most Common Words in \"description\""}
single_word_acc <- desc_accident %>% 
  filter(Fatalities > 0) %>%
  select(description) %>%
  unnest_tokens(word, description) %>% 
  anti_join(stop_words, by="word") %>%
  filter(!is.na(word)) %>%
  group_by(word) %>%
  count() %>% ungroup() %>%
  mutate(rank = min_rank(desc(n))) %>%
  filter(rank <= 30) %>%
  arrange(rank)
# set the color of the word cloud
pal = brewer.pal(8,"Pastel2")
# plot the word cloud
set.seed(1)
single_word_acc %>%
  with(wordcloud(word, n, max.words = nrow(single_word_acc), colors = pal))
```

__str_detect()__ helps select the air accidents related to Boeing and Airbus. The accidents with and without fatalities are included. After using __unnest_tokens()__ to tokenize the __desciption__ and removing the stop words, I group the records by word and count their frequency. Top 30 words are selected to present in a word cloud (Figure 8).

The bigger the word is, the more often it appears in the __description__. The top 3 largest words, "aircraft", "flight" and "crew", almost contain no information of the accidents because they're commonly used in articles related to plane. The fourth most common word, "approach", may indicate that the air accidents occur during the approach, the flight phase shown to have the most air accidents (Figure 1).

On the other hand, the words that appear less frequently can be the main reasons for air accidents. "weather" may indicate bad weather, "control" may be part of "loss of control", and "fire" may imply that the there was fire on the plane. These words make more sense than the words with top frequency. Nevertheless, single words can be from different paraphrases and cannot indicate the true causes. So, the complete paraphrases seem more favorable to me. Therefore, I'd like to try bigram and trigram in the following parts.

## Bigram

```{r bigram.count, echo=FALSE, fig.cap="Word Cloud for Top 15 Most Common Bigrams in \"description\""}
bigram_acc <- desc_accident %>%
  filter(Fatalities > 0) %>%
  select(description) %>%
  unnest_tokens(word, description) %>% 
  filter(!is.na(word)) %>%
  anti_join(stop_words, by="word") %>%
  mutate(id = row_number()) %>%
  spread(id, word) %>%
  unite(col = "description", sep=" ") %>%
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>%
  group_by(bigram) %>%
  count() %>% ungroup() %>%
  mutate(rank = min_rank(desc(n))) %>%
  # filter(rank <= 30) %>%
  arrange(rank)
# plot the word cloud
set.seed(1)
bigram_acc %>%
  with(wordcloud(bigram, n, max.words = 15, colors = pal))
```

For bigram and trigram model, I don't want to filter out all the phrases that contain some stop words. Though they mean nothing when they're single words, they can make up phrases that provide information. For example, there is an "of" inside "lack of fuel", and it's a stop word. If I remove all the phrases that contain stop words, I must lose some valuable information, or even miss the leading factor in air accidents. Therefore, I decide remove all the stop words from __description__ before converting the __descripiton__ to bigram or trigram using __unnest_tokens()__. 

First, __unnest_tokens()__ is used to split the __description__ into single words. Then, __anti_join()__ is utilized to remove the stop words. After that, __spread()__ along with __unite()__ helps recover the description but with no stop word.

Without stop words, we lose the structure of phrases. However, sometime we can recover the original phrases using our knowledge. Though the biggest word, "flight crew", in Figure 9 is uninformative, "weather conditions" and "poor weather" are two phrases with high frequency in the __description__ of fatal air accidents, which implies that bad weather may be highly related to air crash. It may not directly cause an air crash, but it can cause problems for the pilots, such as low visibility, and increase the chance that human make mistakes. 

## Trigram

```{r trigram.count, echo=FALSE}
trigram_acc <- desc_accident %>%
  filter(Fatalities > 0) %>%
  select(description) %>%
  unnest_tokens(word, description) %>% 
  filter(!is.na(word)) %>%
  anti_join(stop_words, by="word") %>%
  mutate(id = row_number()) %>%
  spread(id, word) %>%
  unite(col = "description", sep=" ") %>%
  unnest_tokens(trigram, description, token = "ngrams", n = 3) %>%
  group_by(trigram) %>%
  count() %>% ungroup() %>%
  mutate(rank = min_rank(desc(n))) %>%
  # filter(rank <= 30) %>%
  arrange(rank)
```

Similarly, we can achieve the frequency of trigrams. It is hard to plot a word cloud for trigrams. So, I decide to list some of the important phrases here. 

Among the top 20, the phrases that make sense include __poor weather conditions__ (1), __controlled flight terrain__ (3), __instrument meteorological conditions__ (4), __aircraft hit ground__ (8), __minimum descent altitude__ (8), __post impact fire__ (8) and __auto feather unit__ (17). The number in the parentheses is the rank for each trigram. 

Some of these trigrams can be interpreted as follows:

__poor weather conditions__ ranks the first. It is consistent with our results in __Bigram__. __controlled flight terrain__ means controlled flight into terrain, or __CFIT__, which occurs "when an airworthy aircraft under the complete control of the pilot is inadvertently flown into terrain, water, or an obstacle" [@sky]. In addition, __instrument meteorological conditions__ indicates low visibility. __post impact fire__ means the fire after air crashes. Moreover, __auto feather unit__ implies low engine power. All of these are the factors that can induce fatal air accidents.

For the details, please see: https://www.skybrary.aero/index.php/Main_Page#operational-issues.

\newpage

## TF-IDF

```{r tf.idf.by.fatal, echo=FALSE}
tf_idf_acc <- desc_accident %>%
  mutate(is_fatal = ifelse(Fatalities > 0, 1, 0)) %>%
  select(is_fatal, description) %>%
  unnest_tokens(word, description) %>% 
  filter(!is.na(word)) %>%
  anti_join(stop_words, by="word") %>%
  group_by(is_fatal) %>%
  mutate(num = row_number()) %>%
  spread(num, word) %>%
  unite(col = "description", -is_fatal, sep=" ") %>%
  unnest_tokens(phrase, description, token = "ngrams", n = 3) %>%
  group_by(is_fatal) %>%
  count(phrase) %>%
  bind_tf_idf(term = phrase, document = is_fatal, n = n) %>% ungroup() %>%
  filter(is_fatal == 1) %>%
  mutate(rank = min_rank(desc(tf_idf))) %>%
  filter(rank <= 10) %>%
  select(phrase, tf_idf, rank) %>%
  arrange(rank) 
# show the kable
knitr::kable(tf_idf_acc, booktabs = TRUE, caption = "Top 10 Phrases Related to Fatal Air Crashes Ranked by TF-IDF")
```

TF stands for Term Frequency, and IDF is short for Inverse Document Frequency. Generally speaking, TF increases the weight of the words with more appearance. On the other hand, IDF panelizes the words that appear in too many documents. 

Although TF-IDF is usually used to find the keywords for documents as an unsupervised learning model, I can divide the __description__ according to __Fatalities__ into two documents. By ranking the __tf_idf__ of each phrase, I'm able to see whether some words are more important than other words in the reports of fatal air accidents, which could be the main causes for the accidents.

Moreover, I choose to use three-word phrases to calculate TF-IDF. However, TF-IDF gives similar results to __Trigram__ and top 10 phrases are shown in Table 2. 

# Conclusion

In the past 10 years, the aviation safety has been improved in terms of the __fatalities per one million passengers__ and __fatal accident rate__. However, __fatalities per one million passengers__ is found to be highly correlated with the number of accidents that involve high-capacity commercial airplanes. Therefore, major aircraft manufacturers, like Boeing and Airbus, must shoulder more responsibilty for their customers, such as passengers, airlines and so on. Factors that are likely to cause fatal air accidents, such as __poor weather conditions__, __controlled flight into terrain__ and __post impact fire__, are detected using text mining techniques. Though it's clear that these terms indicate dangerous situations, the true causes still remain unrevealed. More advanced text mining techniques are required to check which factors are critical for these fatal accidents, human factor, technical failure, or others. 

\newpage

# References

---
nocite: |
  @iata1, @iata2, @baaa
...


